%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Ankit Singh} \\ \vspace{1pt}
    SMQ S-57 Air Force Station Hindan Ghaziabad 201004 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9140093041 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shubhamankit1234567890@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ankit-singh-583b1b252//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ankit-singh}}  ~
    \href{https://github.com/Ankit-Singh1234}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Ankit-Singh1234}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions, Ghaziabad}{Sep. 2022 -- June 2026}
      {Bachelor of Technology in Computer Science And Engineering, CGPA: 8.33}{Ghaziabad, Uttar Pradesh}
    \resumeSubheading
      {Air Force School Hindan}{Aug. 2021 -- June 2022}
      {Intermediate with PCM and Computer Science (Python), 96.2\% (School Topper)}{Ghaziabad, Uttar Pradesh}
    \resumeSubheading
      {Bal Academy School}{July 2019 -- June 2020}
      {High School – 93.83\% (School Topper)}{Jodhpur, Rajasthan}
\resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS & EXTRACURRICULAR-----------
\section{Achievements \& Extracurricular}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Competitive Programming}{: Solved 450+ DSA problems on LeetCode, earned 4 badges; 3-Star problem solver in C++ on HackerRank; Master badge in Coding Ninjas.} \\  
        \textbf{Hackathons \& Events}{: Participated in Technical Fest "InnoTech", Hackathons, Programmer of the Month (CSE Department), Tech Seminars, BootCamps, LinkedIn Learning.} \\  
        \textbf{Leadership \& Mentorship}{: NSCC Club Coordinator, conducted multiple bootcamps, and guided juniors and teammates in coding.} \\  
        \textbf{Competitive Exams}{: Qualified for State-Level Quiz Competition (RBI), cleared Government Written Exams (Indian Air Force).} \\  
    }}
\end{itemize}
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{MongoDB Node.js Developer Intern}{May 2024 -- June 2024}
{}{Remote}
\resumeItemListStart
\resumeItem{Designed and built a full-stack web application integrating MongoDB, a Node.js backend, and a React frontend.}
\resumeItem{Implemented CRUD operations and data indexing, enhancing database efficiency and scalability.}
\resumeItem{Collaborated with a team to ensure secure and efficient database operations.}
\resumeItemListEnd

\resumeSubheading
{Full Stack Web Development Intern : MLSA KIET}{Oct 2024 -- Nov 2024}
{MLSA KIET}{Ghaziabad, Uttar Pradesh}
\resumeItemListStart
\resumeItem{Gained hands-on experience in front-end and back-end web development using Node.js, Express.js, and MongoDB.}
\resumeItem{Built medium and advanced-level projects, integrating React.js for a dynamic user interface.}
\resumeItem{Followed best coding practices, including Git/GitHub, agile development, and responsive UI/UX design.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-10pt}


%-----------PROJECTS-----------
\section{Technical Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Banking Management System} $|$ \emph{DBMS, MySQL, Python}}{January 2025}
%           \resumeItemListStart
%             \resumeItem{Engineered a Python-based Bank Management System leveraging MySQL for relational data persistence.}
%             \resumeItem{Designed and implemented secure CRUD operations using parameterized queries to prevent SQL injection.}
%             \resumeItem{Integrated multi-threading for concurrent transaction processing and optimized database indexing for performance.}

% }
%           \resumeItemListEnd
%           \vspace{-13pt}
\resumeProjectHeading
    {\textbf{OneTapPay – One-Tap Digital Payment} $|$ \emph{MERN Stack (MongoDB, Express,React Node.js), UPI SDK}}{jan 2025}
    \resumeItemListStart
        \resumeItem{Seamless digital payment application using the MERN stack, enabling one-tap transactions via UPIand bank cards.}
        \resumeItem{Implemented secure transaction handling with JWT authentication and AES encryption to ensure data protection.}
        \resumeItem{Integrated QR code scanning for merchant payments, bill payments, and real-time transaction history tracking.}
    \resumeItemListEnd
    \vspace{-13pt}


      \resumeProjectHeading
          {\textbf{SwiftCart – Fast and shopping.} $|$ \emph{HTML,CSS,Javascript,MongoDB,ExpressJS,React,NodeJS}}{November 2024}
          \resumeItemListStart
            \resumeItem{SwiftCart is a high-performance MERN stack eCommerce platform, built with React.js and Node.js + Express.js for a seamless user experience.}
            \resumeItem{JWT-based authentication, Bcrypt password hashing, and Role-Based Access Control for secure user access.}
            \resumeItem{Utilizes MongoDB (NoSQL) for efficient data management, ensuring fast and scalable product handling.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Banking Management System} $|$ \emph{DBMS, MySQL, Python}}{January 2025}
          \resumeItemListStart
            \resumeItem{Engineered a Python-based Bank Management System leveraging MySQL for relational data persistence.}
            \resumeItem{Designed and implemented secure CRUD operations using parameterized queries to prevent SQL injection.}
            \resumeItem{Integrated multi-threading for concurrent transaction processing and optimized database indexing for performance.}

}
          \resumeItemListEnd
          \vspace{-13pt}

    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:C/C++, Python, Java, , HTML/CSS, JavaScript, SQL} \\
     \textbf{WebDev}{: React, Tailwind CSS, MongoDB, ExpressJS, NodeJS } \\
     \textbf{Database}{: MongoDB , MySQL} \\
     \textbf{Tools}{: Git/GitHub, VS Code, Eclipse, Canva, Jupyter, PyCharm ,Replit} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------

        
    \resumeSubHeadingListEnd


\end{document}
